Thesis: draft

### 2021-03-31 draft.tex
implemented lay-out feedback from Yolan, part 2

\usepackage{wrapfig}              % meer controle over figuren
\usepackage{floatrow}
\usepackage[format=hang]{caption}
\usepackage{listings}                   % voor mooie code
\usepackage{amsmath, amssymb, amsfonts} % om wiskunde te typen
\usepackage{scalerel}                   % om symbolen te schalen
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{bm}                         % Wiskundesymbolen vet met commando \bm{}
\usepackage{libertine}                  % lettertype
\usepackage{inconsolata}                % lettertype code
\usepackage[T1]{fontenc}                % betere lettertype encodering voor talen met accenten
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{units}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{titlesec}
\usepackage{bbold}
\usepackage{algorithm}
\usepackage{physics}
\usepackage{interval}
\usepackage[colorlinks,citecolor=NavyBlue,linkcolor=NavyBlue% 
,urlcolor=NavyBlue,linktocpage=true,bookmarks=false,hypertexnames=true]{hyperref} 
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{xfrac}
\floatname{algorithm}{Algoritme}

@@

The clustering coefficient is another important measure of network topology. It is a measure for the number of triangles in a network and determines the connectivity in the neighborhood of a node $i$: if a node $i$ has a high clustering coefficient, its neighbors are likely to be directly connected to each other \cite{Li2017}. \\Here a triangle is defined as a loop of length three, this is a sequence of nodes $x, y, z, x$ such that $\{x, y\}, \{y, z\}$ and $\{z, x\}$ are edges of the network. The clustering coefficient is thus a way to measure the degree to which nodes in a network tend to cluster \cite{Li2017}. The local clustering coefficient of a node $i$ is defined as

@@

A connected triple is defined as a set of three nodes with at least two edges between them, so that each node can be reached from the other two (either directly or indirectly). The factor three arises from the fact that each triangle contributes to three different connected triples in the network: one centered at each node in the triangle \cite{F.Costa2007}. Let us denote the number of triangles as $N_{\Delta}$ and the number of connected triples as $N_3$. These two numbers can be obtained from the adjacency matrix in the following way \cite{F.Costa2007}

@@

Network communities are another feature that (complex) networks may posses. A community inside a network is loosely defined as a set of nodes that are more densely connected to nodes inside that set than to the other nodes in the network \cite{Saha2015}. More strictly, a community is defined based on two hypotheses: the connectedness hypothesis and the density hypothesis \cite{Albert2016}. In short, the connectedness hypothesis means that each member of a community should be reached through each other member of the same community \cite{Albert2016}. The density hypothesis implies that nodes inside a community are more likely to be linked to other nodes inside that community than to nodes outside the community \cite{Albert2016}. The density hypothesis narrows what could be considered a community, but it doesn't uniquely define it. Several community definitions are consistent with the density hypothesis. Let us consider three possible definitions: maximum cliques, strong communitoes and weak communities \cite{Albert2016}.\\
\newline
\textbf{Maximum cliques}\\
\newline
A clique is a complete subgraph, where a complete subgraph is defined as a set of nodes of the network where each node in the set is directly connected to all the others nodes in the same set \cite{Albert2016}. A community based on this definition would then be the largest clique in the network. This definition of community might, however, be too restrictive and, beside that, large cliques don't appear very frequent in networks \cite{Albert2016}.\\   
\newline
\textbf{Strong communities}\\
\newline
A strong community is defined such that each node inside the community has more edges to other nodes inside the same community than to nodes outside the community \cite{Albert2016}. Let us denote a community as $C$ and let $i$ be a node inside the community $C$. If we define the internal degree $k_i^{\textrm{int}}(C)$ as the number of edges that connect node $i$ with other nodes in $C$ and the external degree $k_i^{\textrm{ext}}(C)$ as the number of edges that connect node $i$ with nodes outside $C$, then we have the following condition for $C$ to be a strong community \cite{Albert2016}
\begin{equation}
	k_i^{\textrm{int}}(C) > k_i^{\textrm{ext}}(C) \qquad \forall i \in C
\end{equation}
\newline
\textbf{Weak communities}\\
\newline
A weak community is a community where the sum of the internal degree of all the nodes in the community exceeds the sum of the external degree of all the nodes in the community \cite{Albert2016}. We thus have the following condition for a weak community $C$ \cite{Albert2016}
\begin{equation}
	\sum_{i \in C} k_i^{\textrm{int}}(C) > \sum_{i \in C}k_i^{\textrm{ext}}(C)
\end{equation}

@@

The number of nodes at a distance $d$ cannot exceed the number of nodes $N$ in the network. We thus obtain the following equation from which the maximum distance or diameter $d_{max}$ can be obtained

@@

	N \approx \left<k\right>^{d_{max}}

@@

	d_{max} \approx \frac{\ln{N}}{\ln{\left<k\right>}}

@@

A more precise calculation can be found in Appendix \ref{ER}, Section \ref{ERdist}. Equation (\ref{diameter}) might, however, be a better approximation to the average distance $\left<d\right>$ between two randomly chosen nodes \cite{Albert2014}. This is because $d_{max}$ is often dominated by a few extreme paths, where $\left<d\right>$ instead is averaged over all node pairs and thus suppresses these fluctuations \cite{Albert2014}. Hence, the average distance of a random network is defined by \cite{Albert2014}

@@

\subsection{Diameter}\label{ERdist}
The expected number of nodes at a distance $d$ from a starting node is \cite{Albert2014}
\begin{equation}\label{dist}
	N(d) = 1 + \left<k\right> + \left<k\right>^2 + ... + \left<k\right>^d = \frac{\left<k\right>^{d+1} - 1}{\left<k\right> - 1}
\end{equation}
$N(d)$ cannot exceed the number of nodes $N$ in the network. The maximum distance or diameter $d_{max}$ of the network can thus be found by setting \cite{Albert2014}
\begin{equation}
	N(d_{max}) \approx N
\end{equation}
If $\left<k\right> \gg 1$, we can neglect the $-1$ terms in Eq. (\ref{dist}), which gives \cite{Albert2014}
\begin{equation}
	N \approx \left<k\right>^{d_{max}}
\end{equation}
and thus the diameter of a random network becomes \cite{Albert2014}
\begin{equation}
	d_{max} \approx \frac{\ln{N}}{\ln{\left<k\right>}}
\end{equation}

@@

\textbf{Clustering coefficient}\\
\newline
A triangle in the regular ring lattice requires two edge traversals in the same direction and one in the opposite direction \cite{Pele2015}. In the regular ring lattice every node has a fixed degree $K$, this means that each node is connected to $K/2$ neighbors on its left and $K/2$ neighbors on its right. It is then clear that the final, backwards step can span at most $K/2$ nodes \cite{Pele2015}; otherwise we would end up at a different node from which we started, which would definitely not form a triangle.\\
Hence, the number of triangles for a given node is given by choosing the two forward target nodes from the $K/2$ possibilities \cite{Pele2015}
\begin{equation}\label{triangle}
	\binom{\frac{K}{2}}{2} = \frac{1}{4} K \bigg(\frac{K}{2} - 1 \bigg)
\end{equation}
The number of connected triples per node is given by choosing two nodes out of the $K$ neighbors \cite{Pele2015}
\begin{equation}\label{triple}
	\binom{K}{2} = \frac{1}{2} K (K-1)
\end{equation}
Since every node in the regular ring lattice is identical, we can easily find the total number of triangles and connected triples in the network by multiplying Eq. (\ref{triangle}) and Eq. (\ref{triple}) with the number of nodes $N$. We then obtain the final result for the clustering coefficient in the regular ring lattice \cite{Pele2015}
\begin{equation}
	\bar{C} = \frac{3\cdot N \frac{1}{4} K \bigg(\frac{K}{2} - 1 \bigg)}{N \frac{1}{2} K (K-1)} = \frac{3(K-2)}{4(K-1)}
\end{equation}
\newline
\textbf{Average distance}\\
\newline
The general formula for the average distance is given by Eq. (\ref{avdist})
\begin{equation}
	l = \frac{1}{N(N-1)} \sum_{i \neq j} d_{ij}
\end{equation}
where the sum runs over the shortest path between every pair of nodes. Assume we have a regular ring lattice with $N$ nodes and each node has $K$ neighbors. Now we can calculate the distance between node $i$ and every other node in the ring lattice
\begin{itemize}
	\item There are $K$ nodes adjacent to node $i$, so there are $K$ nodes with a distance $d_{ij} = 1$
	\item There are $K$ nodes that are neighbors of the neighbors of node $i$, so there are $K$ nodes with a distance $d_{ij} = 2$
	\item ...
	\item There are $K$ nodes that have a distance $d_{ij} = \frac{N}{K}$ between them and node $i$; its easy to see that these are the nodes that are the furthest away from node $i$ 
\end{itemize}  
So the average distance for node $i$ becomes \cite{chap9}
\begin{equation}
	l_i = \frac{1}{N-1} K \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg) \approx \frac{K}{N} \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg)
\end{equation}
where the last approximation holds for $N \gg 1$. Since every node in the regular ring lattice is identical we can easily find the average distance of the network \cite{chap9}
\begin{equation}
	l = \frac{1}{N} \sum_i l_i = \frac{1}{N} N l_i \approx \frac{K}{N} \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg)
\end{equation}
Using \cite{chap9}
\begin{equation}
	1 + 2+ 3 +...+ x = \sum_{i = 1}^x i = \frac{x(x+1)}{2} \approx \frac{x^2}{2}
\end{equation}
where the last approximation again holds for $x \gg 1$; we finally obtain \cite{chap9}
\begin{equation}
	l \approx \frac{K}{N} \frac{\frac{N^2}{K^2}}{2} = \frac{N}{2K}
\end{equation}

>>>>

\usepackage{wrapfig}              % meer controle over figuren
\usepackage{floatrow}
\usepackage[format=hang]{caption}
\usepackage{listings}                   % voor mooie code
\usepackage[fleqn]{amsmath} 
\usepackage{amssymb, amsfonts} % om wiskunde te typen
\usepackage{scalerel}                   % om symbolen te schalen
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{bm}                         % Wiskundesymbolen vet met commando \bm{}
\usepackage{libertine}                  % lettertype
\usepackage{inconsolata}                % lettertype code
\usepackage[T1]{fontenc}                % betere lettertype encodering voor talen met accenten
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{units}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{titlesec}
\usepackage{bbold}
\usepackage{algorithm}
\usepackage{physics}
\usepackage{interval}
\usepackage[colorlinks,citecolor=NavyBlue,linkcolor=NavyBlue% 
,urlcolor=NavyBlue,linktocpage=true,bookmarks=false,hypertexnames=true]{hyperref} 
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{xfrac}
\floatname{algorithm}{Algoritme}

@@

The clustering coefficient is another important measure of network topology. It is a measure for the number of triangles in a network and determines the connectivity in the neighborhood of a node $i$: if a node $i$ has a high clustering coefficient, its neighbors are likely to be directly connected to each other \cite{Li2017}. \\
A triangle is defined as a loop of length three, this is a sequence of nodes $x, y, z, x$ such that $\{x, y\}, \{y, z\}$ and $\{z, x\}$ are edges of the network. The clustering coefficient is thus a way to measure the degree to which nodes in a network tend to cluster \cite{Li2017}. The local clustering coefficient of a node $i$ is defined as

@@

A connected triple is defined as a set of three nodes with at least two edges between them, so that each node can be reached from the other two (either directly or indirectly). The factor three arises from the fact that each triangle contributes to three different connected triples in the network: one centered at each node in the triangle \cite{F.Costa2007}. \\
Let us denote the number of triangles as $N_{\Delta}$ and the number of connected triples as $N_3$. These two numbers can be obtained from the adjacency matrix in the following way \cite{F.Costa2007}

@@

Network communities are another feature that (complex) networks may posses. A community inside a network is loosely defined as a set of nodes that are more densely connected to nodes inside that set than to the other nodes in the network \cite{Saha2015}. More strictly, a community is defined based on two hypotheses: the connectedness hypothesis and the density hypothesis \cite{Albert2016}. In short, the connectedness hypothesis means that each member of a community should be reached through each other member of the same community \cite{Albert2016}. The density hypothesis implies that nodes inside a community are more likely to be linked to other nodes inside that community than to nodes outside the community \cite{Albert2016}. The density hypothesis narrows what could be considered a community, but it doesn't uniquely define it. Several community definitions are consistent with the density hypothesis. Let us consider three possible definitions: maximum cliques, strong communitoes and weak communities \cite{Albert2016}.\\
\newline
\textbf{Maximum cliques}\\
\newline
A clique is a complete subgraph, where a complete subgraph is defined as a set of nodes of the network where each node in the set is directly connected to all the others nodes in the same set \cite{Albert2016}. A community based on this definition would then be the largest clique in the network. This definition of community might, however, be too restrictive and, beside that, large cliques don't appear very frequent in networks \cite{Albert2016}.\\   
\newpage
\noindent
\textbf{Strong communities}\\
\newline
A strong community is defined such that each node inside the community has more edges to other nodes inside the same community than to nodes outside the community \cite{Albert2016}. Let us denote a community as $C$ and let $i$ be a node inside the community $C$. If we define the internal degree $k_i^{\textrm{int}}(C)$ as the number of edges that connect node $i$ with other nodes in $C$ and the external degree $k_i^{\textrm{ext}}(C)$ as the number of edges that connect node $i$ with nodes outside $C$, then we have the following condition for $C$ to be a strong community \cite{Albert2016}
\begin{equation}
	k_i^{\textrm{int}}(C) > k_i^{\textrm{ext}}(C) \qquad \forall i \in C
\end{equation}
\newline
\textbf{Weak communities}\\
\newline
A weak community is a community where the sum of the internal degree of all the nodes in the community exceeds the sum of the external degree of all the nodes in the community \cite{Albert2016}. We thus have the following condition for a weak community $C$ \cite{Albert2016}
\begin{equation}
	\sum_{i \in C} k_i^{\textrm{int}}(C) > \sum_{i \in C}k_i^{\textrm{ext}}(C)
\end{equation}

@@

The number of nodes at a distance $d$ cannot exceed the number of nodes $N$ in the network. We thus obtain the following equation from which the maximum distance or diameter $d_{\textrm{max}}$ can be obtained

@@

	N \approx \left<k\right>^{d_{\textrm{max}}}

@@

	d_{\textrm{max}} \approx \frac{\ln{N}}{\ln{\left<k\right>}}

@@

A more precise calculation can be found in Appendix \ref{ER}, Section \ref{ERdist}. Equation (\ref{diameter}) might, however, be a better approximation to the average distance $\left<d\right>$ between two randomly chosen nodes \cite{Albert2014}. This is because $d_{\textrm{max}}$ is often dominated by a few extreme paths, where $\left<d\right>$ instead is averaged over all node pairs and thus suppresses these fluctuations \cite{Albert2014}. Hence, the average distance of a random network is defined by \cite{Albert2014}

@@

\subsection{Diameter}\label{ERdist}
The expected number of nodes at a distance $d$ from a starting node is \cite{Albert2014}
\begin{equation}\label{dist}
	N(d) = 1 + \left<k\right> + \left<k\right>^2 + ... + \left<k\right>^d = \frac{\left<k\right>^{d+1} - 1}{\left<k\right> - 1}
\end{equation}
$N(d)$ cannot exceed the number of nodes $N$ in the network. The maximum distance or diameter $d_{max}$ of the network can thus be found by setting \cite{Albert2014}
\begin{equation}
	N(d_{\textrm{max}}) \approx N
\end{equation}
If $\left<k\right> \gg 1$, we can neglect the $-1$ terms in Eq. (\ref{dist}), which gives \cite{Albert2014}
\begin{equation}
	N \approx \left<k\right>^{d_{\textrm{max}}}
\end{equation}
and thus the diameter of a random network becomes \cite{Albert2014}
\begin{equation}
	d_{\textrm{max}} \approx \frac{\ln{N}}{\ln{\left<k\right>}}
\end{equation}

@@

\textbf{Clustering coefficient}\\
\newline
A triangle in the regular ring lattice requires two edge traversals in the same direction and one in the opposite direction \cite{Pele2015}. In the regular ring lattice every node has a fixed degree $K$, this means that each node is connected to $K/2$ neighbors on its left and $K/2$ neighbors on its right. It is then clear that the final, backwards step can span at most $K/2$ nodes \cite{Pele2015}; otherwise we would end up at a different node from which we started, which would definitely not form a triangle.\\
Hence, the number of triangles for a given node is given by choosing the two forward target nodes from the $K/2$ possibilities \cite{Pele2015}
\begin{equation}\label{triangle}
	\binom{\frac{K}{2}}{2} = \frac{1}{4} K \bigg(\frac{K}{2} - 1 \bigg)
\end{equation}
The number of connected triples per node is given by choosing two nodes out of the $K$ neighbors \cite{Pele2015}
\begin{equation}\label{triple}
	\binom{K}{2} = \frac{1}{2} K (K-1)
\end{equation}
Since every node in the regular ring lattice is identical, we can easily find the total number of triangles and connected triples in the network by multiplying Eq. (\ref{triangle}) and Eq. (\ref{triple}) with the number of nodes $N$. We then obtain the final result for the clustering coefficient in the regular ring lattice \cite{Pele2015}
\begin{equation}
	\left<C\right> = \frac{3\cdot N \frac{1}{4} K \bigg(\frac{K}{2} - 1 \bigg)}{N \frac{1}{2} K (K-1)} = \frac{3(K-2)}{4(K-1)}
\end{equation}
\newline
\textbf{Average distance}\\
\newline
The general formula for the average distance is given by Eq. (\ref{avdist})
\begin{equation}
	l = \frac{1}{N(N-1)} \sum_{i \neq j} d_{ij}
\end{equation}
where the sum runs over the shortest path between every pair of nodes. Assume we have a regular ring lattice with $N$ nodes and each node has $K$ neighbors. Now we can calculate the distance between node $i$ and every other node in the ring lattice
\begin{itemize}
	\item There are $K$ nodes adjacent to node $i$, so there are $K$ nodes with a distance $d_{ij} = 1$
	\item There are $K$ nodes that are neighbors of the neighbors of node $i$, so there are $K$ nodes with a distance $d_{ij} = 2$
	\item ...
	\item There are $K$ nodes that have a distance $d_{ij} = \frac{N}{K}$ between them and node $i$; its easy to see that these are the nodes that are the furthest away from node $i$ 
\end{itemize}  
So the average distance for node $i$ becomes \cite{chap9}
\begin{equation}
	l_i = \frac{1}{N-1} K \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg) \approx \frac{K}{N} \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg)
\end{equation}
where the last approximation holds for $N \gg 1$. Since every node in the regular ring lattice is identical we can easily find the average distance of the network \cite{chap9}
\begin{equation}
	l = \frac{1}{N} \sum_i l_i = \frac{1}{N} N l_i \approx \frac{K}{N} \bigg(1 + 2 + 3 + ... + \frac{N}{K} \bigg)
\end{equation}
Using \cite{chap9}
\begin{equation}
	1 + 2+ 3 +...+ x = \sum_{i = 1}^x i = \frac{x(x+1)}{2} \approx \frac{x^2}{2}
\end{equation}
where the last approximation again holds for $x \gg 1$; we finally obtain \cite{chap9}
\begin{equation}
	l \approx \frac{K}{N} \frac{\frac{N^2}{K^2}}{2} = \frac{N}{2K}
\end{equation}
